---
title: "Wildlife Recovery Analysis"
author: "Middleton Lab"
date: "12/10/2021"
output: html_document
---

# Wildlife Recovery Project Analysis

Set working directory...
```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls()) 

wd_path <- "C:/repos/wildlife_recovery"

setwd(wd_path)

knitr::opts_knit$set(root.dir = wd_path) 
```

Load required packages...
```{r packages, include = FALSE, warning = FALSE}
# Make a list of the packages we need, check whether they're installed, and install the ones we're missing...
required.pkg <- c("tidyverse", "magrittr", "data.table", "Hmisc", "googledrive", "googlesheets4", "splitstackshape", "aod", "sjPlot", "sjmisc", "sjlabelled", "gtsummary", "jtools", "JointAI", "multcomp", "factorplot")
pkgs.not.installed <- required.pkg[!sapply(required.pkg, function(p) require(p, character.only=T))]
if(length(pkgs.not.installed) > 0) install.packages(pkgs.not.installed, dependencies=TRUE)

# Load the required libraries...
lapply(required.pkg, library, character.only = TRUE) 

options(scipen=999)
```

## Download and Clean Data

### Download Google Sheet Data 

Raw data is stored in a google sheet on the Middleton Lab Google Drive.. To make this easy, I've made the sheet public. If this section isn't working, the first thing to do is to check to make sure that document is still public. This link is to data that has already been manually cleaned.

```{r}
#This let's us download the public spreadsheet without having to authorize your account:
drive_deauth()  
#Download edited data directly from google sheet "Edited Wildlife recovery case study data" in Datasheets folder:
drive_download("https://docs.google.com/spreadsheets/d/15yYexIiG3WSeTfnAwUJBgrwrDk9zPtsRqdlAlVcm6fI/edit?usp=sharing",
               overwrite = TRUE,
               path = "data/goog_raw.csv")
#Save locally:
datasheet <- fread('data/goog_raw.csv')
```

### Split Columns
```{r, warning = FALSE}
colsToSplit <- c("IUCN Threats", "Goals (Ecological)", "Goals (Socioeconomic)", "Goals (Admin/Logistical)",
                 "Success Indicators (Ecological)", "Success Indicators (Socioeconomic)", 
                 "Success Indicators (Admin/Logistical)",  "Translocation Type", 
                 "Captive/wild/rehab", "Post Release","Land ownership", "Site Land Type", "Groups involved", "Outreach", 
                 "Major difficulties faced (Ecological)",      "Major difficulties faced (Socioeconomic)" , 
                 "Major difficulties faced (Admin/Logistic)" , "Lessons learned (Ecological)" ,             
                 "Lessons learned (Socioeconomic)",  "Lessons learned (Admin/Logistic)",  "Reasons cited for success (Ecological)", 
                 "Reasons Cited for Success (Socioeconomic)", "Reasons cited for success (Admin/Logistic)",
                 "Local threats", "Outcome")

#function to split column into multiple columns containing 0/1 values for each unique value in original column
splitColumn <- function (colName) {
  datasheet %>% select(colName) %>% cSplit_e(1, ",", type = "character", fill = 0, drop = TRUE)
}

#merged all split up columns
datasheetSplit <- map_dfc(colsToSplit, splitColumn) %>% cbind()
```

#### Split Goals
```{r}
#Species Level Goal: “Reinforce Population”, “Restore Population” “Connect Populations” 
#“Population Growth” “Behavior” “Genetics” “Distribution” “Survival” “Reproduction”
datasheetSplit <- datasheetSplit %>%
  mutate(speciesLevelGoal = ifelse(`Goals (Ecological)_Reinforce Population` |
                                     `Goals (Ecological)_Restore Population` |
                                     `Goals (Ecological)_Connect Populations` |
                                     `Goals (Ecological)_Population Growth` |
                                     `Goals (Ecological)_Behavior` |
                                     `Goals (Ecological)_Genetics` |
                                     `Goals (Ecological)_Distribution` |
                                     `Goals (Ecological)_Survival` |
                                     `Goals (Ecological)_Reproduction`, T, F))

#Ecological Goal: “Habitat”, “Interaction”, “Function”
datasheetSplit <- datasheetSplit %>%
  mutate(ecologicalGoal = ifelse(`Goals (Ecological)_Habitat` |
                                   `Goals (Ecological)_Interaction` |
                                   `Goals (Ecological)_Function`, T, F))

#Socioeconomic Goal: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomicGoal = ifelse(`Goals (Socioeconomic)_Cultural Benefit` |
                                      `Goals (Socioeconomic)_Economic Benefit` |
                                      `Goals (Socioeconomic)_Education` |
                                      `Goals (Socioeconomic)_Engage Locals in Conservation` |
                                      `Goals (Socioeconomic)_Increase awareness` |
                                      `Goals (Socioeconomic)_Increase Social Tolerance` |
                                      `Goals (Socioeconomic)_Law Enforcement` |
                                      `Goals (Socioeconomic)_other`, T, F))

#Admin/Logistical Goal: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(adminLogisticalGoal = ifelse(`Goals (Admin/Logistical)_Funding` |
                                        `Goals (Admin/Logistical)_Husbandry` |
                                        `Goals (Admin/Logistical)_Institutional` |
                                        `Goals (Admin/Logistical)_Procedural` |
                                        `Goals (Admin/Logistical)_Reduce Human Intervention`, T, F))
```


#### Split Indicators
```{r}
#Species Level Indicator: “Reinforce Population”, “Restore Population”,
#“Connected Populations” “Increase Population Growth” “Behavior”,
#“Genetics” “Distribution” “Survival” “Reproduction”
datasheetSplit <- datasheetSplit %>%
  mutate(speciesLevelIndicator = ifelse(`Success Indicators (Ecological)_Reinforce Population` |
                                          `Success Indicators (Ecological)_Restore Population` |
                                          `Success Indicators (Ecological)_Connected Populations` |
                                          `Success Indicators (Ecological)_Increase Population Growth` |
                                          `Success Indicators (Ecological)_Behavior` |
                                          `Success Indicators (Ecological)_Genetics` |
                                          `Success Indicators (Ecological)_Distribution` |
                                          `Success Indicators (Ecological)_Survival` |
                                          `Success Indicators (Ecological)_Reproduction`, T, F))

#Ecological Indicator: “Habitat”, “Interaction”, “Function”
datasheetSplit <- datasheetSplit %>%
  mutate(ecologicalIndicator = ifelse(`Success Indicators (Ecological)_Habitat` |
                                        `Success Indicators (Ecological)_Interaction` |
                                        `Success Indicators (Ecological)_Function`, T, F))

#Socioeconomic Indicator: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomicIndicator = ifelse(`Success Indicators (Socioeconomic)_Cultural Benefit` |
                                           `Success Indicators (Socioeconomic)_Economic Benefit` |
                                           `Success Indicators (Socioeconomic)_Increase Public Awareness` |
                                           `Success Indicators (Socioeconomic)_Increase Social Tolerance` |
                                           `Success Indicators (Socioeconomic)_Legal Protection` |
                                           `Success Indicators (Socioeconomic)_Public Involvement`, T, F))

#Admin/Logistical Indicator: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(adminLogisticalIndicator = ifelse(`Success Indicators (Admin/Logistical)_Husbandry` |
                                             `Success Indicators (Admin/Logistical)_Institutional` |
                                             `Success Indicators (Admin/Logistical)_Procedural` |
                                             `Success Indicators (Admin/Logistical)_Reduce Human Intervention`, T, F))

#Species Level Difficulty: “Reinforce Population”, “Restore Population”, “Connect Populations”
#"Population Growth” “Behavior” “Genetics” “Distribution” “Survival” “Reproduction”
datasheetSplit <- datasheetSplit %>%
  mutate(speciesLevelDifficulty = ifelse(`Major difficulties faced (Ecological)_Reinforce Population` |
                                           `Major difficulties faced (Ecological)_Restore Population` |
                                           `Major difficulties faced (Ecological)_Connect Populations` |
                                           `Major difficulties faced (Ecological)_Population Growth` |
                                           `Major difficulties faced (Ecological)_Behavior` |
                                           `Major difficulties faced (Ecological)_Genetics` |
                                           `Major difficulties faced (Ecological)_Distribution` |
                                           `Major difficulties faced (Ecological)_Survival` |
                                           `Major difficulties faced (Ecological)_Reproduction`, T, F))

#Ecological Difficulty: “Habitat”, “Interaction”, “Function”
datasheetSplit <- datasheetSplit %>%
  mutate(ecologicalDifficulties = ifelse(`Major difficulties faced (Ecological)_Habitat` |
                                           `Major difficulties faced (Ecological)_Interaction` |
                                           `Major difficulties faced (Ecological)_Function`, T, F))

#Socioeconomic Difficulty: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomicDifficulty = ifelse(`Major difficulties faced (Socioeconomic)_Acceptance/Social Tolerance` |
                                            `Major difficulties faced (Socioeconomic)_Economic Benefit` |
                                            `Major difficulties faced (Socioeconomic)_Human disturbance` |
                                            `Major difficulties faced (Socioeconomic)_human-caused mortality` |
                                            `Major difficulties faced (Socioeconomic)_human-casued mortality` |
                                            `Major difficulties faced (Socioeconomic)_Legal Involvement` |
                                            `Major difficulties faced (Socioeconomic)_Legal Protection` |
                                            `Major difficulties faced (Socioeconomic)_other` |
                                            `Major difficulties faced (Socioeconomic)_Public Awareness` |
                                            `Major difficulties faced (Socioeconomic)_Public Involvement`, T, F))

```

#### Split Lessons Learned
```{r}
#Species Level Lesson Learned: “Reinforce Population”, “Restore Population”,
#“Connect Populations” “Population Growth” “Behavior” “Genetics” “Distribution”,
#“Survival” “Reproduction”
datasheetSplit <- datasheetSplit %>%
  mutate(speciesLevelLessons = ifelse(`Lessons learned (Ecological)_Reinforce Population` |
                                        `Lessons learned (Ecological)_Restore Population` |
                                        `Lessons learned (Ecological)_Connect Populations` |
                                        `Lessons learned (Ecological)_Population Growth` |
                                        `Lessons learned (Ecological)_Behavior` |
                                        `Lessons learned (Ecological)_Genetics` |
                                        `Lessons learned (Ecological)_Distribution` |
                                        `Lessons learned (Ecological)_Survival` |
                                        `Lessons learned (Ecological)_Reproduction`, T, F))

#Ecological Lesson Learned: “Habitat”, “Interaction”, “Function”
datasheetSplit <- datasheetSplit %>%
  mutate(ecologicalLessons = ifelse(`Lessons learned (Ecological)_Habitat` |
                                      `Lessons learned (Ecological)_Interaction` |
                                      `Lessons learned (Ecological)_Function`, T, F))

#Socioeconomic Lesson Learned: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomicLessons = ifelse(`Lessons learned (Socioeconomic)_Increase Acceptance/Social Tolerance` |
                                         `Lessons learned (Socioeconomic)_Economic Benefit` |
                                         `Lessons learned (Socioeconomic)_Investing in human-wildlife conflict mitigation is critical` |
                                         `Lessons learned (Socioeconomic)_Cultural Benefit` |
                                         `Lessons learned (Socioeconomic)_Legal Protection` |
                                         `Lessons learned (Socioeconomic)_other` |
                                         `Lessons learned (Socioeconomic)_Increase Public Awareness` |
                                         `Lessons learned (Socioeconomic)_Public Involvement`, T, F))

#Admin/Logistical Lesson Learned: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(adminLogisticalLessons = ifelse(`Lessons learned (Admin/Logistic)_Husbandry` |
                                           `Lessons learned (Admin/Logistic)_devoted leader` |
                                           `Lessons learned (Admin/Logistic)_Funding` |
                                           `Lessons learned (Admin/Logistic)_Institutional` |
                                           `Lessons learned (Admin/Logistic)_Procedural` |
                                           `Lessons learned (Admin/Logistic)_Reduce Human Intervention`, T, F))
```


#### Split Reasons for Success
```{r}
#Species Level Success: “Reinforce Population”, “Restore Population”, “Connected Populations”,
#“Population Growth” “Restored Behavior” “Restored Genetics” “Increased Distribution”
#“Survival” “Reproduction”
datasheetSplit <- datasheetSplit %>%
  mutate(speciesLevelReasons = ifelse(`Reasons cited for success (Ecological)_Reinforce Population` |
                                        `Reasons cited for success (Ecological)_Restore Population` |
                                        `Reasons cited for success (Ecological)_Connected Populations` |
                                        `Reasons cited for success (Ecological)_Population Growth` |
                                        `Reasons cited for success (Ecological)_Restored Behavior` |
                                        `Reasons cited for success (Ecological)_Restored Genetics` |
                                        `Reasons cited for success (Ecological)_Increased Distribution` |
                                        `Reasons cited for success (Ecological)_Survival` |
                                        `Reasons cited for success (Ecological)_Reproduction`, T, F))

#Ecological Success: “Restored Habitat”, “Restored Interaction”, “ Restored Function”
datasheetSplit <- datasheetSplit %>%
  mutate(ecologicalReasons = ifelse(`Reasons cited for success (Ecological)_Restored Habitat` |
                                      `Reasons cited for success (Ecological)_Restored Interaction` |
                                      `Reasons cited for success (Ecological)_Restored Function`, T, F))

#Socioeconomic Success: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomicReasons = ifelse(`Reasons Cited for Success (Socioeconomic)_Cattle production` |
                                         `Reasons Cited for Success (Socioeconomic)_Cultural Benefit` |
                                         `Reasons Cited for Success (Socioeconomic)_Economic Benefit` |
                                         `Reasons Cited for Success (Socioeconomic)_Increase Acceptance/Social Tolerance` |
                                         `Reasons Cited for Success (Socioeconomic)_Increase Public Awareness` |
                                         `Reasons Cited for Success (Socioeconomic)_Legal Protection` |
                                         `Reasons Cited for Success (Socioeconomic)_litigation against the program` |
                                         `Reasons Cited for Success (Socioeconomic)_other` |
                                         `Reasons Cited for Success (Socioeconomic)_political difficulties` |
                                         `Reasons Cited for Success (Socioeconomic)_Public Involvement`, T, F))

#Admin/Logistical Success: if anything is included (including other)
datasheetSplit <- datasheetSplit %>%
  mutate(adminLogisticalReasons = ifelse(`Lessons learned (Admin/Logistic)_Husbandry` |
                                           `Lessons learned (Admin/Logistic)_Funding` |
                                           `Lessons learned (Admin/Logistic)_Institutional` |
                                           `Lessons learned (Admin/Logistic)_Procedural` |
                                           `Lessons learned (Admin/Logistic)_Reduce Human Intervention`, T, F))
```

#### Socioeconomic Summaries
```{r}
#Goals_indicator: If the case study included a socio-economic goal or success indicator
datasheetSplit <- datasheetSplit %>%
  mutate(Goals_indicator = ifelse(socioeconomicGoal | socioeconomicIndicator, T, F))

#Outreach: any outreach
datasheetSplit <- datasheetSplit %>%
  mutate(outreach = ifelse(`Outreach_Education/Capacity Building` |
                             `Outreach_Indigenous groups engagement` |
                             `Outreach_landowner engagement` |
                             `Outreach_landowner incentives` |
                             `Outreach_Local Outreach` |
                             `Outreach_Media Campaign`, T, F))

#Goals_indicator_outreach: if the case study included a socio-economic goal, 
#success indicator, or had any outreach
datasheetSplit <- datasheetSplit %>%
  mutate(Goals_indicator_outreach = ifelse(socioeconomicGoal | socioeconomicIndicator | 
                                             outreach, T, F))


#socioeconomic_difficulty: if the case study did not include a socio-economic goal 
#or success indicator, but cited a socio-economic difficulty 
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic_difficulty = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                             socioeconomicDifficulty, T, F))

#Socioeconomic2_difficulty: if the case study did not include a socio-economic goal, 
#indicator and did not have any outreach, but cited a socio-economic difficulty
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic2_difficulty = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                              !outreach & socioeconomicDifficulty, T, F))

#socioeconomic_lessonLearned: if the case study did not include a socio-economic goal 
#or success indicator, but cited a socio-economic lesson learned  
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic_lessonLearned = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                                socioeconomicLessons, T, F))

#Socioeconomic2_lessonLearned: if the case study did not include a socio-economic goal, 
#indicator and did not have any outreach, but cited a socio-economic lesson learned
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic2_lessonLearned = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                                 !outreach & socioeconomicLessons, T, F))

#socioeconomic_success: if the case study did not include a socio-economic goal or 
#success indicator, but cited a socio-economic reason for success  
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic_success = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                          socioeconomicReasons, T, F))

#Socioeconomic2_success: if the case study did not include a socio-economic goal, 
#indicator and did not have any outreach, but cited a socio-economic reason for success
datasheetSplit <- datasheetSplit %>%
  mutate(socioeconomic2_success = ifelse(!socioeconomicGoal & !socioeconomicIndicator &
                                           !outreach & socioeconomicReasons, T, F))


#Outcome summaries
datasheetSplit <- datasheetSplit %>%
  mutate(outcome_binary = ifelse(`Outcome_Reproduction` |
                                   `Outcome_Viable population` |
                                   `Outcome_Population increase` |
                                   `Outcome_Survival`, T, F))



#Make species-level, ecological, and admin summaries 
datasheetSplit <- datasheetSplit %>%
  mutate(species_Goals_indicator = ifelse(speciesLevelGoal | speciesLevelIndicator, T, F))

datasheetSplit <- datasheetSplit %>%
  mutate(ecological_Goals_indicator = ifelse(ecologicalGoal | ecologicalIndicator, T, F))

datasheetSplit <- datasheetSplit %>%
  mutate(adminLogistical_Goals_indicator = ifelse(adminLogisticalGoal | adminLogisticalIndicator, T, F))



#combine datasets
Data <- cbind(datasheet, datasheetSplit)
```

## Analyze Data!

#### Percent of case studies that included HDs in each of the following categories:
```{r}
sum(ifelse(Data$Goals_indicator == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$Goals_indicator_outreach == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$adminLogistical_Goals_indicator == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$species_Goals_indicator == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$ecological_Goals_indicator == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$socioeconomic_difficulty == TRUE, 1, 0))/nrow(Data)*100
sum(ifelse(Data$socioeconomic_lessonLearned == TRUE, 1, 0))/nrow(Data)*100
```

### Logit Regression Models

#### Run big global model: I (Mitch) didn't actually used this though
```{r}
HD_logit <- glm(Goals_indicator ~ Continent + Taxonomy + `Local Conservation Status` + `IUCN Threats_Agriculture or aquaculture` + `IUCN Threats_Biological resource use` + `IUCN Threats_Climate Change or Severe Weather` + `IUCN Threats_Energy production or mining` + `IUCN Threats_Human Intrusion and Disturbance` + `IUCN Threats_Invasives or Disease` + `IUCN Threats_Natural System Modifications` + `IUCN Threats_Pollution` + `IUCN Threats_Residential/commercial development` + `IUCN Threats_Transportation and service corridors` + `Groups involved_Academic` + `Groups involved_Government` + `Groups involved_Local community/indigenous groups` + `Groups involved_Non-profit` + `Groups involved_Private company` + `Groups involved_Private landowners` + `Groups involved_Zoo` + `Site Land Type_Protected Area` +  `Site Land Type_Suburban/Rural` + `Site Land Type_Urban` + `Site Land Type_Working Land` , data = Data, family = "binomial")
summary(HD_logit)
```

#### Logistic regression for continents
```{r}
continent_logit <- glm(Goals_indicator ~ as.factor(Continent), data = Data, family = "binomial")
summary(continent_logit)
confint(continent_logit)

c <- factorplot(continent_logit)
print(c, digits=3, sig = FALSE)
plot(c)

continent_logit2 <- glm(outcome_binary ~ as.factor(Continent), data = Data, family = "binomial")
summary(continent_logit2)
confint(continent_logit2)
c <- factorplot(continent_logit2)
print(c, digits=3, sig = FALSE)
plot(c)
```

#### Contour Plot of Logistic Regression
```{r, warning = FAlSE}
#If you want to relevel anything (but not needed with the pairwise comps)
Data$Continent<-factor(Data$Continent, levels=c("Oceania", "Africa", "Asia", 
                                                "Europe", "North America", "South America"))


#Plot
cont_plot <- effect_plot(continent_logit, pred = Continent, interval = TRUE, x.label = "Continent", y.label = "Probability of a Including HD", colors = "seagreen", line.thickness = 2)


cont_plot <- data.frame(cont_plot[1])

ggplot(cont_plot, aes(y=data.Goals_indicator, x=data.Continent))+
  geom_point(color = "purple", size = 10)+ ## This adds the line
  geom_errorbar(aes(ymax=data.ymax, ymin=data.ymin), width=0.2, color = "black", size = 4)+
  xlab("")+ ## This adds x label
  ylab("Probability of Including HD")+ ## This adds y axis
  theme(text = element_text(size = 15)) + ylim(0,1)
```

#### Logistic regression for taxonomy
```{r}
taxa_logit <- glm(Goals_indicator ~ as.factor(Taxonomy), data = Data, family = "binomial")
summary(taxa_logit)
confint(taxa_logit)
t <- factorplot(taxa_logit)
print(t, digits=3, sig = FALSE)
plot(t)

taxa_logit2 <- glm(outcome_binary ~ as.factor(Taxonomy), data = Data, family = "binomial")
summary(taxa_logit2)
confint(taxa_logit2)
t <- factorplot(taxa_logit2)
print(t, digits=3, sig = FALSE)
plot(t)


#Relevel if you want...again didn't use this
Data$Taxonomy<-factor(Data$Taxonomy, levels=c("Fish", "Reptile", "Amphibian", "Bird", "Mammal"))

#Plot Taxa
plot_taxa <- effect_plot(taxa_logit, pred = Taxonomy, interval =TRUE, x.label = "Taxa", y.label = "Probability of a Including HD", colors = "seagreen", line.thickness = 2)

plot_taxa2 <- data.frame(plot_taxa[1])

ggplot(plot_taxa2, aes(y=data.Goals_indicator, x=data.Taxonomy))+
  geom_point(color = "purple", size = 10)+ ## This adds the line
  geom_errorbar(aes(ymax=data.ymax, ymin=data.ymin), width=0.2, color = "black", size = 4)+
  xlab("")+ ## This adds x label
  ylab("Probability of Including HD")+ ## This adds y axis
  theme(text = element_text(size = 15)) + ylim(0,1)
```

#### Logistic regression to see if case studies with a history of conflict are more likely to include HD
```{r}
Data$`Conflict/tolerance issue?` <- ifelse(Data$`Conflict/tolerance issue?`=="Yes",1,0)
conflict_logit <- glm(Goals_indicator ~ `Conflict/tolerance issue?`, data = Data, family = "binomial")
summary(conflict_logit)
confint(conflict_logit)


#Logistic regression looking at temporal trends (might want to remove case study from the 20s)
temporal_logit <- glm(Goals_indicator ~ `Reintroduction start year`, data = Data, family = "binomial")
summary(temporal_logit)
confint(temporal_logit)

effect_plot(temporal_logit, pred = `Reintroduction start year`, interval = TRUE, y.label = "Probability of Including HD")
```

#### Logistic Regression looking at the inclusion of HD by positive/negative outcome
```{r}
outcome3_logit <- glm(outcome_binary ~ Goals_indicator, data = Data, family = "binomial")
summary(outcome3_logit)
confint(outcome3_logit)


outcome_plot <- effect_plot(outcome3_logit, pred = Goals_indicator, interval =TRUE, x.label = "Inclusion of HD", y.label = "Probability of a Positive Outcome", colors = "seagreen", line.thickness = 2)

outcome_plot <- data.frame(outcome_plot[1])

ggplot(outcome_plot, aes(y=data.outcome_binary, x=data.Goals_indicator))+
  geom_point(color = "purple", size = 5)+ ## This adds the line
  geom_errorbar(aes(ymax=data.ymax, ymin=data.ymin), width=0.2, color = "black", size = 2)+
  xlab("Inclusion of HD")+ ## This adds x label
  ylab("Probability of a Positive Outcome")+ ## This adds y axis
  theme(text = element_text(size = 15)) + ylim(.5,1)

```

#### Logisitc regression for inclusion of HD by groups involved
```{r}
#make groups involved long-form. Need to do this because most case studies have multiple groups involved 
groups_involved <- select(Data, outcome_binary, Goals_indicator, `Groups involved`)
groups_involved <- separate_rows(groups_involved, `Groups involved`, sep = ",")
groups_involved$outcome_binary <- ifelse(groups_involved$outcome_binary=="TRUE",1,0)
groups_involved <- groups_involved %>% mutate(across(where(is.character), str_trim))

#For Indicator
group_logit <- glm(Goals_indicator ~ as.factor(`Groups involved`), data = groups_involved, family = "binomial")
summary(group_logit)
confint(group_logit)
c <- factorplot(group_logit)
print(c, digits=5, sig = TRUE)
plot(c)

#For Outcome
group_logit2 <- glm(outcome_binary ~ as.factor(`Groups involved`), data = groups_involved, family = "binomial")
summary(group_logit2)
confint(group_logit2)
c <- factorplot(group_logit2)
print(c, digits=5, sig = TRUE)
plot(c)
```

#### Logisitc regression for inclusion of HD by threats
```{r}
#make threats long form. Need to do this because most species have multiple threats
threats <- select(Data, Goals_indicator, `IUCN Threats`, outcome_binary)
threats <- separate_rows(threats, `IUCN Threats`, sep = ",")
threats$Goals_indicator <- ifelse(threats$Goals_indicator=="TRUE",1,0)
threats <- threats %>% mutate(across(where(is.character), str_trim))

#For Indicators
threats_logit <- glm(Goals_indicator ~ as.factor(`IUCN Threats`), data = threats, family = "binomial")
summary(threats_logit)
confint(threats_logit)
c <- factorplot(threats_logit)
print(c, digits=5, sig = TRUE)
plot(c)

#For Outcomes
threats_logit2 <- glm(outcome_binary ~ as.factor(`IUCN Threats`), data = threats, family = "binomial")
summary(threats_logit2)
confint(threats_logit2)
c <- factorplot(threats_logit2)
print(c, digits=5, sig = TRUE)
plot(c)
```


